Suplementary Material 3: Run Simulations on the Last Birth Omited Data

### 2023-04-05 S3_run_simulations_EE_not_last.Rmd
aproximate RAM usage

```{r}
## Identify number of CPU cores available for parallel computing,
## note: using a large number may lead RAM to max out, so you may have to adjust
## that according to your infrastructure:
nb_cores <- min(c(20L, parallel::detectCores() - 1))

@@

library(twinR)
library(doSNOW)
nb_cores <- min(c(20L, parallel::detectCores() - 1)) ## only 20 since large memory footprint
timeout <- 24 * 60 * 60 # a Day

@@

   name_obj <- paste0("slopes_under_", scenario)
   targetFname <- paste0(slopeDir,"/", name_obj, ".rda")
   if(!file.exists(targetFname)){
     slopes_under_scenario <- simulate_slopes_for_GOF(N_replicates_level1 = 200L,
                                                      N_replicates_level2 = 49L,
                                                     birth_level_data = data_births_monthly,
                                                      life_history_fits = fits,
                                                      scenario = scenario,
                                                      nb_cores = nb_cores,
                                                      timeout = timeout,
                                                      .log = TRUE, lapply_pkg = "pbmcapply",
                                                      verbose = list(fit = TRUE, simu = FALSE))
     rm(fits)
     assign(name_obj, value = slopes_under_scenario)
     save(list = name_obj, file = targetFname)
     rm(list = name_obj) # remove the object behind the name!
     rm(slopes_under_scenario, scenario, name_obj) # remove the object directly
     gc_stuff <- gc(verbose = FALSE)
   }

>>>>

The memory (RAM) and usage is quite high for simulations. Below there are some information about the RAM  usages per  CPU of simulations on Estonian data w/o last birth. The total number of CPUs used for running these simulations was 61.

Memory usage per CPU:

  * base model: about 15GB (dumped cores have a size range 12-23GB)

```{r}
## Identify number of CPU cores available for parallel computing,
## note: using a large number may lead RAM to max out, so you may have to adjust
## that according to your infrastructure:
nb_cores <- min(c(200L, parallel::detectCores() - 1))

#it seems that simulating the base model for Estonian not last birth data
#requires about 15GB of RAM per CPU core (tested with 61 CPU cores)

@@

library(twinR)
library(doSNOW)
#it seems that simulating the base model for Estonian not last birth data
#requires about 15GB of RAM per CPU core (tested with 61 CPU cores)

timeout <- 24 * 60 * 60 # a Day

@@

   name_obj <- paste0("slopes_under_", scenario)
   targetFname <- paste0(slopeDir,"/", name_obj, ".rda")
   if(!file.exists(targetFname)){
     slopes_under_scenario <- simulate_slopes_for_GOF(N_replicates_level1 = 200L,
                                                      N_replicates_level2 = 20L,
                                                     birth_level_data = data_births_monthly,
                                                      life_history_fits = fits,
                                                      scenario = scenario,
                                                      nb_cores = nb_cores,
                                                      timeout = timeout,
                                                      .log = TRUE, lapply_pkg = "pbmcapply",
                                                      verbose = list(fit = TRUE, simu = FALSE))
     rm(fits)
     assign(name_obj, value = slopes_under_scenario)
     save(list = name_obj, file = targetFname)
     rm(list = name_obj) # remove the object behind the name!
     rm(slopes_under_scenario, scenario, name_obj) # remove the object directly
     gc_stuff <- gc(verbose = FALSE)
   }
